MCTS Based on Simple Regret

### 2012-01-21 paper/rmcts/aaai/paper.tex
lots of changes to graphics

\begin{dfn} Scheme $\mathbf{UCB(\alpha)}$ repeatedly pulls arm $i$ that maximizes 
upper confidence bound $b_i$ on the reward:
\begin{equation}
b_i=\overline X_i+\sqrt {\frac {\alpha \ln n} {n_i}}
\end{equation}
where $\overline X_i$ is the average reward obtained from arm $i$,
$n_i$ is the number of times arm $i$ was pulled, and $n$ is the total
number of pulls so far. \end{dfn} The best known upper bound on the simple
regret of $UCB(\alpha)$ is polynomially decreasing in the number of samples
(see \cite{Bubeck.pure}, Theorems~2,3).

An upper bound on the simple regret of uniform sampling is
exponentially decreasing in the number of samples (see
\cite{Bubeck.pure}, Proposition~1). However, empirically
$UCB(\alpha)$ yields a lower simple regret than uniform
sampling.

@@

\begin{thm} Simple regret of the $UCB_{\sqrt{}}(\alpha)$ sampling
  scheme is asymptotically bounded from above as.
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le ...
\end{equation}
\end{thm}
\begin{proof}[Proof sketch:] TODO
\end{proof}

@@

UCT \cite{Kocsis.uct} is a generalization of UCB for MCTS.  UCT
applies UCB at each step of a rollout.  We suggest an improvement on
UCT, which combines different sampling schemes on the first step and
during the rest of a rollout:
\begin{dfn}
The \textbf{SR+CR MCTS sampling scheme} selects an action at the
current root node according to a scheme suitable for minimizing 
simple regret (\textbf{SR}), such as $\frac 1 2$-greedy or $UCB_{\sqrt{\cdot}}$, and
then selects actions according to $UCB$, minimizing cumulative regret (\textbf{CR}).
\end{dfn}

@@

The results were empirically verified on Multi-armed Bandit instances,
on search trees, and on the sailing domain, as defined in \cite{Kocsis.uct}. The
experiments confirmed the hypotheses. The algorithms used in the
experiments are:
\begin{description}
\item[RND:] uniform \underline{r}a\underline{nd}om samping;
\item[UCT:] \underline{U}pper \underline{C}onfidence Bounds applied to
  \underline{T}rees \cite{Kocsis.uct};
\item[RCT:] U\underline{CT} with the first step replaced with uniform
  \underline{r}andom sampling;
\item[GCT:] U\underline{CT} with the first step
  replaced with $\frac 1 2$-\underline{g}reedy sampling;
\item[QCT:] U\underline{CT} with the first step
  replaced with U\underline{Q}B.
\end{description}

@@

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.8]{twolevel-tree.pdf}\\
    a. search tree
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.4]{tree-identity-k=16-uqb=8.pdf}\\ 
    b. 16 arms
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.4]{tree-identity-k=64-uqb=8.pdf} \\
    c. 64 arms
  \end{minipage}
  \label{fig:mcts-regret}
  \caption{MCTS: a path to the best arm}
\end{figure}

>>>>

\begin{dfn} Scheme $\mathbf{UCB(\alpha)}$ repeatedly pulls arm $i$ that maximizes 
upper confidence bound $b_i$ on the reward:
\begin{equation}
b_i=\overline X_i+\sqrt {\frac {\alpha \ln n} {n_i}}
\end{equation}
where $\overline X_i$ is the average reward obtained from arm $i$,
$n_i$ is the number of times arm $i$ was pulled, and $n$ is the total
number of pulls so far. \end{dfn} The best known upper bound on the simple
regret of UCB($\alpha$) is polynomially decreasing in the number of samples
(see \cite{Bubeck.pure}, Theorems~2,3).

An upper bound on the simple regret of uniform sampling is
exponentially decreasing in the number of samples (see
\cite{Bubeck.pure}, Proposition~1). However, empirically
UCB($\alpha$) yields a lower simple regret than uniform
sampling.

@@

\begin{thm} Simple regret of the UCB$_{\sqrt{}}$($\alpha$) sampling
  scheme is asymptotically bounded from above as.
\begin{equation}
\IE r_{ucb\sqrt{\cdot}} \le ...
\end{equation}
\end{thm}
\begin{proof}[Proof sketch:] TODO
\end{proof}

@@

UCT \cite{Kocsis.uct} is a generalization of UCB for MCTS.  UCT
applies UCB at each step of a rollout.  We suggest an improvement on
UCT, which combines different sampling schemes on the first step and
during the rest of a rollout:
\begin{dfn}
The \textbf{SR+CR MCTS sampling scheme} selects an action at the
current root node according to a scheme suitable for minimizing 
simple regret (\textbf{SR}), such as $\frac 1 2$-greedy or UCB$_{\sqrt{\cdot}}$, and
then selects actions according to UCB, minimizing cumulative regret (\textbf{CR}).
\end{dfn}

@@

The results were empirically verified on Multi-armed Bandit instances,
on search trees, and on the sailing domain, as defined in
\cite{Kocsis.uct}. In most cases, the experiments showed lower average
simple regret for $\frac 1 2$-greedy an UCB$_{\sqrt{\cdot}}$ than for
UCB on sets, and for the SR+CR scheme than for UCT in trees.

@@

\begin{figure}[h!]
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.8]{twolevel-tree.pdf}\\
    a. search tree
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.5]{tree-identity-k=16-uqb=8.pdf}\\ 
    b. 16 arms
    \vspace{1em}
  \end{minipage}
  \begin{minipage}[c]{1.0\linewidth}
    \centering
    \includegraphics[scale=0.5]{tree-identity-k=64-uqb=8.pdf} \\
    c. 64 arms
  \end{minipage}
  \label{fig:mcts-regret}
  \caption{MCTS: a path to the best arm}
\end{figure}
